### 2022-11-14 NSF2022/Description/backgroundv3.tex

The field of self-organization encompasses a broad range of
interesting and challenging phenomena in engineering and science.
For example, understanding the
organization of lipids and proteins in vesicles is crucial to
designing effective drug carriers
and functional mimics of cells
\cite{Marui2022IncreasedEO,https://doi.org/10.1002/adma.202206288}.
The COVID-19 pandemic has led to a
concerted effort to understand
the mechanisms of RNA condensation by structural proteins
that control virus structure
\cite{Kim2021SelfassembledMV}.
Engineers have developed superior techniques
that rely on nanoscale  
capillary and van der Waals forces
to print high-resolution
features on devices \cite{Zeng20223DprintedMT}.
Finally, researchers design efficient algorithms for
constructing interaction kernels in the to study 
of agent-based systems like swarms and flocking
\cite{Lu2019NonparametricIO,Tadmor2021OnTM}.

@@

When fluids are involved,
tracking self-organization
becomes difficult due to the deformability of
suspended media in the presence of non-local hydrodynamic interactions.  
The phase field method,
a prominent approach in this area,
introduce a scalar-valued phase
field function for the volume fraction of
amphiphilic lipids or polymers in solvent, for example.
Sometimes called the diffuse interface
method, one devises energy functionals involving the gradient and
well-potentials of the phase field, and possibly convolution
kernels, to characterize the self- and solvent-interaction of the
suspended media 
\cite{Promislow2022UndulatedBI,C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16,Choksi2003OnTD}.
Because the fluid interfaces are given by 
level-sets of a smooth function,
they can have almost arbitrary topology
e.g., free ends, junctions
\cite{Promislow2017ExistenceBA,Promislow2022UndulatedBI},
the evolution equations can be studied
by well-established variational and analytical tools,
\cite{Gavish2011CurvatureDF,Dai2019WeakSF,Dai2015CompetitiveGE,
Dai2022GeometricEO,Dai2020MinimizersFT,Dai2013GeometricEO},
and the governing equations are amenable to numerical approximation
\cite{Christlieb2020BenchmarkCO,Christlieb2019CompetitionAC}.
One of the downsides, though, 
is that granular details like molecular heterogeneity
and orientations that may be crucial to the physics at mesoscopic scales, are
clumsy to incorporate in the model. Moreover,
numerical simulations of
phase field models typically discretize the entire fluid domain, a
nd apply cutoff boundary conditions when periodic
domains are not under consideration.

The PIs recently developed a new mathematical model of
self-organization in fluid systems~\cite{FuQuRyYo22,fu-ryh-qua-you2022,Fu2018_SIAM}.
The framework uses small, rigid bodies called ``granules''
to represent parcels of suspended media.
The granule shapes and boundary conditions
capture the local properties of the suspension,
and instead of volume fraction, a phase field function represents
the properties of the solvent.
Our approach falls into the category of work that considers
particles as a discretization of a continuous problem;
in this case one is dealing with a particle
method, as an alternative to other discretization methods
such as finite-difference, finite-element, and spectral methods
\cite{Wilson2021ComparisonOT}.
We have departed from the terminology
``particles'', though, to emphasize the role played the granules' finite size.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize
  (a) Granules make a superstructure e.g., a vesicle. The panel shows
  the moving domain $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$,
  and the unit inward normal $\nu.$ Panels b, c, d show the
  interplay between the phase field $\phi$ (colormap) and granule configuration.
  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) = \tfrac{1}{2}\phi^2$.
  The white arrows are the fluid velocity field.
  The panels reach an equilibrium state in panel d.
  }
\end{figure}

@@

To determine how the granules move through space,
we look for rigid body transformations
\begin{align}
\label{eq:RBT}
  F_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{dF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \omega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = F_i(\XX,t)$.  Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu \,\dif s = \mathbf{0}
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations 
describing the velocity $\uu$ and pressure $p$ of
the incompressible fluid region with viscosity $\mu$.
Equation~\eqref{eqn:phase} describes the
transitions of the scalar order parameter $\phi$ with a decay length
$\epsilon$.
The scalar function $W(\phi) : \mathbb{R} \to \mathbb{R}$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$,  etc.,
representing metastable states of the solvent.
In the single-well case, $W(\phi) = \frac{1}{2}\phi^2$
has the minimum $\phi_0 = 0$ and the phase field equation
\eqref{eqn:phase} becomes the \emph{linear} screened Laplace equation.
In the double-well case e.g, $W(\phi) = \frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$,
the phase field equation \eqref{eqn:phase} takes the form of an
Allen-Cahn equation with local minima $\phi_0 < 0 < \phi_1$.
Section \ref{sec:specificaim1} discusses certain
modifications needed for \eqref{eqn:phase} in the nonlinear case.

@@

For the moving domain, equations~\eqref{eqn:noslip}
specify a no-slip boundary condition for a rigid body with translation
velocity $\aa'_i(t) = \vv_i$ and angular velocity $\omega_i$ (the axial
vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at the solvent-granule interface. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balances
the force and torque 
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
and we interpret the ``cross product'' as $\aa \times \bb = (\aa^{\perp} \cdot
\bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
(-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad range
of nonspecific self-organization phenomena in surface chemistry, biology
and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label
(\S\ref{sec:specificaim1}, equation \eqref{eq:amphiphilic_BC})
spontaneously self-organize to sequester the hydrophobic fluid phase
(Figure~\ref{fig:flow_map}). Changes in the boundary conditions result
in distint morphologies (Figure~\ref{fig:self-assembly2}) whose rheology
can be further investigate (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their
SIAM Multiscale Modeling and Simulation and Journal of Fluid Mechanics works
\cite{Fu2018_SIAM, FuQuRyYo22}
is the problem of \emph{vesicle hydrodynamics}.
A vesicle is a small, fluid filled membrane sack.
The goal in vesicle hydrodynamics is to study flow patterns 
arrising from the interaction
between membrane elasticity and the fluid.

\begin{wrapfigure}[10]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic
simulations is their fidelity to physics.
The model contains a few
parameters; granule radius $c$,
decay length $\epsilon$,
surface tension $\gamma$.
When these are set to realistic values 
\cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian, Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016},
we quantitatively recover many of the well-known
elastic moduli for single-component lipid bilayers
\cite{Nagle17, Nagle17-2, LeVeWa14,NAGLE2000159}. 
Such agreement is a validation that equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} 
correctly capture the

\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}
\noindent long-range interactions between amphiphilic
granules (such as lipid macromolecules) surfaces.

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continous, permeable, inextensible,
elastic vesicle.
The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading vesicle
\cite{Finken2008, Shaqfeh11} (see Figure \ref{fig:JPv_linearshear}).
Movies of Figure \ref{fig:JPv_linearshear} reveal intermonolayer slip
and derived values for intermonolayer friction are in good quantitative
agreement those derived by atomistic and Martini force field simulation
studies \cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure \ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear rate
\cite{VLAHOVSKA2009775,keller_skalak_1982}. A side-by-side comparison of
granule-based vesicles and the sharp interface representation yielded
shapes and trajectories that basically overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
is highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension driven fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[18]{r}{3.1in}
  \vspace{-0pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes}
and~\eqref{eqn:phase} are challenging to develop because of
the complicated and unbounded domain.
This challenge is compounded when dense
suspensions are considered. Integral equations (IEs) offer an
alternative formulation of the PDEs that only require meshing the
boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and the automatically satisfy far-field
conditions. Additional advantages of discretizations of IE
formulations include high-order, or even spectral, accuracy and
well-conditioned linear system that can be solved iteratively with a
mesh-independent number of Krylov iterations such as the generalized
minimal residual method (GMRES). However, IEs have challenges: nearly
touching granules requires a quadrature rule for nearly-singular
integrals; their discretization results in dense matrices; and they
cannot immediately be applied to non-linear PDEs.
\S~\ref{sec:specificaim2} discusses
a variety of tools the IE community,
including PI Quaife, has developed
to address these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
%\begin{align}
%\label{eq:energy_law}
%  \begin{split}
%  \frac{d}{dt}E
%    &= - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
%  \uu^T|^2 \,d\xx, \\
%    E &= \gamma \int_{\Omega(t)}
%  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
%  \end{split}
%\end{align}
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by the phase transitions
between the granule boundaries and the solvent and the energy law states that
the granules move to decrease energy,
which is lost due to viscous dissipation.
The derivation of \eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$
and $\Omega(t)$. It uses the Rayleigh Transport Theorem to write the time
derivative of $E$ as an energy density flux through the boundary
involving the phase stress $T_i$, and a bulk term involving the Euler-Lagrange
derivative of $E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
Furthermore, the integral of the 
phase stress vectors $T_i\nu$ over $\partial \Omega$ is zero.
Figure~\ref{fig:coarsening} summarizes the general evolution of $E$ from the
self-assembly process to
the collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-30pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
\end{wrapfigure}

>>>>

The field of self-organization encompasses a broad range of interesting
and challenging phenomena in engineering and science. For example,
understanding the organization of lipids and proteins in vesicles is
crucial to designing effective drug carriers and functional mimics of
cells~\cite{Marui2022IncreasedEO,
https://doi.org/10.1002/adma.202206288}. The COVID-19 pandemic has led
to a concerted effort to understand the mechanisms of RNA condensation
by structural proteins that control virus
structure~\cite{Kim2021SelfassembledMV}. Engineers have developed
superior techniques that rely on nanoscale capillary and van der Waals
forces to print high-resolution features on
devices~\cite{Zeng20223DprintedMT}. Finally, researchers design
efficient algorithms for constructing interaction kernels in the to
study of agent-based systems like swarms and
flocking~\cite{Lu2019NonparametricIO, Tadmor2021OnTM}.

@@

When fluids are involved, tracking self-organization becomes difficult
due to the deformability of suspended media in the presence of non-local
hydrodynamic interactions. The phase field method, a prominent approach
in this area, introduces a scalar-valued phase field function for the
volume fraction of amphiphilic lipids or polymers in solvent, for
example. Sometimes called the diffuse interface method, one devises
energy functionals involving the gradient and well-potentials of the
phase field, and possibly convolution kernels, to characterize the self-
and solvent-interaction of the suspended
media~\cite{Promislow2022UndulatedBI, C9SM01983A,doi:10.1063/5.0009734,
LiAn-Chang16, Choksi2003OnTD}. Because the fluid interfaces are given by
level-sets of a smooth function, they can have almost arbitrary topology
e.g., free ends, junctions~\cite{Promislow2017ExistenceBA,
Promislow2022UndulatedBI}, the evolution equations can be studied by
well-established variational and analytical
tools~\cite{Gavish2011CurvatureDF, Dai2019WeakSF, Dai2015CompetitiveGE,
Dai2022GeometricEO, Dai2020MinimizersFT, Dai2013GeometricEO}, and the
governing equations are amenable to numerical
approximation~\cite{Christlieb2020BenchmarkCO,
Christlieb2019CompetitionAC}. One of the downsides, though, is that
granular details like molecular heterogeneity and orientations that may
be crucial to the physics at mesoscopic scales, are clumsy to
incorporate in the model. Moreover, numerical simulations of phase field
models typically discretize the entire fluid domain, and apply cutoff
boundary conditions when periodic domains are not under consideration.

The PIs recently developed a new mathematical model of self-organization
in fluid systems~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM}. The
framework uses small, rigid bodies called ``granules'' to represent
parcels of suspended media. The granule shapes and boundary conditions
capture the local properties of the suspension, and instead of volume
fraction, a phase field function represents the properties of the
solvent. Our approach falls into the category of work that considers
particles as a discretization of a continuous problem; in this case one
is dealing with a particle method, as an alternative to other
discretization methods such as finite-difference, finite-element, and
spectral methods~\cite{Wilson2021ComparisonOT}. We have departed from
the terminology ``particles'', though, to emphasize the role played the
granules' finite size.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/Background/Domain.pdf}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[width=0.45\textwidth]{figures/SpecificAim1/3Particles.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/Domain.jpg}
%    \includegraphics[keepaspectratio,height=2.7cm]{figures/SpecificAim1/3Particles.jpg}
  \end{center}
  \caption{\label{fig:flow_map} \footnotesize (a) Granules make a
  superstructure e.g., a vesicle. The panel shows the moving domain
  $\Omega(t)$, granules with centers $\aa_i$ and directors $\dd_i$, and
  the unit inward normal $\nnu$. Panels (b), (c), (d) show the interplay
  between the phase field $\phi$ (colormap) and granule configuration.
  Red is for $\phi = 1$ and blue for $\phi = 0$; $W(\phi) =
  \tfrac{1}{2}\phi^2$. The white arrows are the fluid velocity field.
  The panels reach an equilibrium state in panel (d).}
\end{figure}

@@

To determine how the granules move through space, we look for rigid body
transformations
\begin{align}
\label{eq:RBT}
  \FF_i(\XX,t) = R_i(t)(\XX - \aa_i(0)) + \aa_i(t),\quad \XX \in U_i(0),
\end{align}
where $i = 1,\ldots,N_b,$ $R_i(t)$ is an $n
\times n$ rotation matrix, $\aa_i(t)$ are the granule centers, and $\XX$ is a
reference coordinate.
The dynamics come from the following system of semi-linear, elliptic boundary value problems:
\begin{alignat}{4}
  \label{eqn:stokes} 
  -\mu\Delta \uu + \nabla p &= \mathbf{0}, 
  \quad \nabla \cdot \uu = 0, &&\xx \in \Omega(t), \\
  \label{eqn:phase}
  -\epsilon^2 \Delta \phi + W'(\phi) &= 0, &&\xx \in \Omega(t),\\
  \label{eqn:noslip}        
  \frac{d\FF_i}{dt}(\XX,t) & = \uu(\xx) = 
    \vv_i + \oomega_i \times (\xx - \aa_i), 
  \quad &&\xx \in \Gamma_i(t),\\
  \label{eqn:material}
  \phi(\xx) &= h_i(\XX),  &&\xx \in \Gamma_i(t),
\end{alignat}
for $i=1,\ldots,N_b$ and where $\xx = \FF_i(\XX,t)$. Finally,
\begin{align}
\label{eqn:stressbalance}
\int_{\Gamma_i} \left(\sigma  + T_i\right)\nnu \,\dif s = \mathbf{0},\quad
\int_{\Gamma_i} (\xx - \aa_i)\times \left(\sigma + T_i\right) \nnu
  \,\dif s = \mathbf{0},
\end{align}
where
\begin{align}
\label{eqn:hydro_stress}
\sigma = \mu(\nabla \uu + \nabla \uu^T) - pI,\quad 
T_i = \gamma\left[\epsilon^{-1} W(\phi)I
  + \epsilon\left(\tfrac{1}{2}|\nabla \phi|^2I - \nabla \phi \nabla
  \phi^T\right)\right]
\end{align}
are the hydrodynamic and phase field stresses, respectively.
Equations~\eqref{eqn:stokes} are the Stokes equations describing the
velocity $\uu$ and pressure $p$ of the incompressible fluid region with
viscosity $\mu$. Equation~\eqref{eqn:phase} describes the transitions
of the scalar order parameter $\phi$ with a decay length $\epsilon$.
The scalar function $W(\phi) : \RR \to \RR$ is a nonnegative
well-potential with local minima $\phi_0, \phi_1$, etc., representing
metastable states of the solvent. In the single-well case, $W(\phi) =
\frac{1}{2}\phi^2$ has the minimum $\phi_0 = 0$ and the phase field
equation~\eqref{eqn:phase} becomes the \emph{linear} screened Laplace
equation. In the double-well case e.g, $W(\phi) =
\frac{1}{4}(\phi^2-1)^2+cx$, $c > 0$, the phase field
equation~\eqref{eqn:phase} takes the form of an Allen-Cahn equation with
local minima $\phi_0 < 0 < \phi_1$. Section \ref{sec:specificaim1}
discusses certain modifications needed for~\eqref{eqn:phase} in the
nonlinear case.

@@

For the moving domain, equations~\eqref{eqn:noslip}
specify a no-slip boundary condition for a rigid body with translation
velocity $\aa'_i(t) = \vv_i$ and angular velocity $\oomega_i$ (the axial
vector for $R'_i(t)R_i(t)^T$) about the point $\aa_i(t) \in U_i(t)$. In
equation~\eqref{eqn:material}, the function $h_i$ is a material label
specifying the phase at the solvent-granule interface. Finally,
equation~\eqref{eqn:stressbalance} closes the system by requiring that
the force and torque generated by hydrodynamic stress balance
the force and torque 
generated by phase stress $T_i$ in~\eqref{eqn:hydro_stress}. The
parameter $\gamma > 0$ is surface tension, $I$ is the identity matrix,
and we interpret the ``cross product'' as $\aa \times \bb = (\aa^{\perp} \cdot
\bb) \kk$ where $\kk = (0,0,1) \in \RR^3$ and $(a_1,a_2)^{\perp} =
(-a_2,a_1)$ whenever $\aa, \bb \in \mathbb{R}^2$.

\subsection{Applications}
Since the framework is scale independent, it can be applied to a broad
range of nonspecific self-organization phenomena in surface chemistry,
biology, and engineering. For one, the
formulation~\eqref{eq:RBT}--\eqref{eqn:stressbalance} captures exactly
the right behavior expected from amphiphilic self-assembly. For example,
three bodies with amphiphilic label (\S\ref{sec:specificaim1}, equation
\eqref{eq:amphiphilic_BC}) spontaneously self-organize to sequester the
hydrophobic fluid phase (Figure~\ref{fig:flow_map}). Changes in the
boundary conditions result in distinct morphologies
(Figure~\ref{fig:self-assembly2}) whose rheology can be further
investigated (\S\ref{sec:specificaim3}).
%
A concrete application the PIs have considered in their SIAM Multiscale
Modeling and Simulation and Journal of Fluid Mechanics
works~\cite{Fu2018_SIAM, FuQuRyYo22} is the problem of \emph{vesicle
hydrodynamics}. A vesicle is a small, fluid filled membrane sack. The
goal in vesicle hydrodynamics is to study flow patterns arising from the
interaction between membrane elasticity and the fluid.

\begin{wrapfigure}[10]{l}{0.48\textwidth}
\vspace{-5pt}
\includegraphics[width=0.48\textwidth]{figures/PreliminaryWork/TankTreading.jpg}
\vspace{-20pt}
\caption{\label{fig:JPv_linearshear} \footnotesize Granular vesicles
  undergo tank-treading in background shear flow.}
\end{wrapfigure}
%
A striking feature of our hydrodynamic simulations is their fidelity to
physics. The model contains a few parameters; granule radius $c$, decay
length $\epsilon$, surface tension $\gamma$. When these are set to
realistic values \cite{Fu2018_SIAM, ErLjCl89, Lin2005, Parsegian,
Israelachvili80, GarciaSaez, KUZMIN2005, Petelska2012,Jackson2016}, we
quantitatively recover many of the well-known elastic moduli for
single-component lipid bilayers \cite{Nagle17, Nagle17-2,
LeVeWa14,NAGLE2000159}. Such agreement is a validation that
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} correctly capture
the long-range interactions between amphiphilic granules (such as lipid
macromolecules) surfaces.
\begin{wrapfigure}[13]{l}{0.475\textwidth}
\vspace{-10pt}
\includegraphics[width=0.475\textwidth]{figures/PreliminaryWork/Rupture.jpg}
\caption{\label{fig:JPv_rupture} \footnotesize Rupture of a granular
  vesicle under large shear rates.}
\end{wrapfigure}

In terms of hydrodynamics, the granule vesicles in background flows
replicate the behaviour of a continuous, permeable, inextensible,
elastic vesicle. The simulations showed, for the first time, a
granule-vesicle suspension behaving as a tank-treading
vesicle~\cite{Finken2008, Shaqfeh11} (see
Figure~\ref{fig:JPv_linearshear}). Movies of
Figure~\ref{fig:JPv_linearshear} reveal intermonolayer slip and derived
values for intermonolayer friction are in good quantitative agreement
those derived by atomistic and Martini force field simulation
studies~\cite{WuoEd06, denOtter2007, SHKULIPA2005823, Zgorski2019}. In
Figure~\ref{fig:JPv_rupture}, membrane rupture occurs at large shear
rates and yields a dimensional scaling for critical rupture shear
rate~\cite{VLAHOVSKA2009775, keller_skalak_1982}. A side-by-side
comparison of granule-based vesicles and the sharp interface
representation yields shapes and trajectories that basically overlapped.

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in
equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is highly desirable
from the Applied Math point of view as there are many \emph{Further
Applications}, such as (i) amphiphilic Janus spheres that form diverse
suprastructures~\cite{HaBr20, McBr21, Bradley2017}, (ii) pickering
emulsions involving two-phase fluids and dense suspensions
\cite{Bradley2016}, (iii) creation and manipulation of small droplets
using amphiphilic microparticles~\cite{Ha2022SurfaceEM,
Ha2020MinimalSC}, and (iv) tension driven fabrication of
microstructures~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,
Zeng20223DprintedMT, Russell2016EnergyLF}.

\subsection{Computational method and mathematical properties}
\begin{wrapfigure}[17]{r}{3.1in}
  \vspace{-8pt}
  \centering
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1.5in]{figures/Background/Peanut/PeanutIE.pdf}\\
  \includegraphics[width=3in]{figures/Background/NSF.pdf}\\
\caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em top left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em top right}) requires meshing only the
  boundary of the domain.
  ({\em bottom}) BIE can handle intricately shaped domains as well.}
\end{wrapfigure}
Computational methods to solve the partial differential equations
(PDEs)~\eqref{eqn:stokes} and~\eqref{eqn:phase} are challenging to
develop because of the complicated and unbounded domain. This challenge
is compounded when dense suspensions are considered. Integral equations
(IEs) offer an alternative formulation of the PDEs that only require
meshing the boundary of the granules rather than all of $\Omega(t)$
(Figure~\ref{fig:fem_vs_bie}), and they automatically satisfy far-field
conditions. Additional advantages of discretizations of IE formulations
include high-order, or even spectral, accuracy and well-conditioned
linear system that can be solved iteratively with a mesh-independent
number of Krylov iterations such as the generalized minimal residual
method (GMRES). However, IEs have challenges: nearly touching granules
requires a quadrature rule for nearly-singular integrals; their
discretization results in dense matrices; and they cannot immediately be
applied to non-linear PDEs. \S\ref{sec:specificaim2} discusses a variety
of tools the IE community, including PI Quaife, has developed to address
these numerical challenges.

In the absence of external flow, the
system~\eqref{eq:RBT}--\eqref{eqn:stressbalance} has the energy law
\begin{align}
\label{eq:energy_law}
  \frac{d}{dt}E
  = - \int_{\Omega(t)}\tfrac{1}{2}\mu|\nabla \uu + \nabla
  \uu^T|^2 \,d\xx,\quad
    E = \gamma \int_{\Omega(t)}
  \frac{\epsilon}{2} |\nabla \phi|^2 + \frac{1}{\epsilon} W(\phi) \,d\xx.
\end{align}
Here $E$ is the energy stored by the phase transitions between the
granule boundaries and the solvent and the energy law states that the
granules move to decrease energy, which is lost due to viscous
dissipation. The derivation of~\eqref{eq:energy_law} is interesting
because $E$ depends both on $\phi$ and $\Omega(t)$. It uses the Rayleigh
Transport Theorem to write the time derivative of $E$ as an energy
density flux through the boundary involving the phase stress $T_i$, and
a bulk term involving the Euler-Lagrange derivative of
$E$~\cite{Fu2018_SIAM}. The Euler-Lagrange derivative vanishes due
to~\eqref{eqn:phase} and the boundary flux transforms into viscous
dissipation due to~\eqref{eqn:hydro_stress} and the Stokes equations.
Furthermore, the integral of the phase stress vectors $T_i\nnu$ over
$\partial \Omega$ is zero. Figure~\ref{fig:coarsening} summarizes the
general evolution of $E$ from the self-assembly process to the
collective dynamics of the assembly under external forcing.

\begin{wrapfigure}[16]{r}{4in} 
  \includegraphics[width=4in]{figures/Background/coarsening.pdf}
  \vspace{-25pt}
  \caption{\label{fig:coarsening} \footnotesize Energy $E$ in
  equation~(\ref{eq:energy_law}) of a suspension of amphiphilic granules
  versus time $t$. Under the moving domain problem
  \eqref{eq:RBT}--\eqref{eqn:hydro_stress} with amphiphilic boundary
  condition, the granules self-organize into vesicle bilayers. External
  hydrodynamic effects are introduced to study elastic properties of
  the granules assembly~\cite{Fu2018_SIAM,FuQuRyYo22}.}
\end{wrapfigure}

We have $\lim_{\xx \to \infty} \phi(\xx) = \phi_0$ in the far field and
when background flows are involved, we require that $\lim_{\xx \to
\infty} \uu(\xx) - \uu_{\infty}(\xx) = \mathbf{0}$, where $\uu_{\infty}$
can take the form
%In the case of shear background flow,
%for example,
%\begin{align}
%\label{eqn:shear_BG_flow}
%\uu_{\infty}(\xx) = \dot{\gamma} \xx \cdot \mathbf{e}_y \mathbf{e}_x,
%\end{align}
%where $\dot \gamma$ is the shear rate and $\mathbf{e}_x$, $\mathbf{e}_y$
%are horizontal and vertical basis vectors, respectively.
%Other
%background flows include
of a shear, extensional, parabolic Poiseuille, or Taylor-Green flow, for
example. For numerical stability, we include pairwise repulsive forces
and torques in~\eqref{eqn:stressbalance} to prevent the near-collision
between neighboring granules. This introduces a repulsive potential in
the energy law~\eqref{eq:energy_law}. Background flow adds elastic
energy to the granule configurations, as illustrated in
Figure~\ref{fig:coarsening}.
%and is quantified by simulation. We refer to the
%PIs work~\cite{FuQuRyYo22, fu-ryh-qua-you2022, Fu2018_SIAM} for details.
